Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-19 paper.tex
did some edits of the paper

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$.
\label{rst:budget}
\end{theorem}

@@

Denote $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$, then $X_{i}$ follows a ``geometric distribution'', which counts the total number of trials before the $i^{th}$ different arm were pulled at time $t=t^{0},t^{0}+1,\cdots$. At each time $t=t^{0}, t^{0}+1,\cdots$, there are two possibilities for a success trial:
\begin{itemize}
\item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $n^{-1}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled. In this case, the probability that the $i^{th}$ different arm will be pulled is 1.  
\item There exists at least $n^{-1}$ proportion of agents who will choose an un-pulled arm as his/her myopic action. In this case, we know each type of agent shows up with probability at least $p$. Thus, the probability that the $i^{th}$ different arm will be pulled is at least $n^{-1}$.
\end{itemize}

@@

\begin{lemma}
For $t\in[t_n,t_{n+1}]$, the expected incentive payment $E[c(t)]$ is bounded above by $\Delta + Nm \sqrt{\frac{2}{n\pi}}$. 
\label{lemma:payment}
\end{lemma}

@@

\begin{align}
&E[c(t)] \nonumber \\
\leq & \Delta \times P(c(t)>0) + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}1\{c(t)>0\}] \nonumber \\
\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}] \nonumber \\
\leq & \Delta + \sum_{j=1}^{m}E[\max_{i}|\epsilon_{i,t}^{j}|] \nonumber \\
\leq & \Delta + \sum_{j=1}^{m}E\left[\sum_{i=1}^{N}|\epsilon_{i,t}^{j}|\right] \nonumber \\
\leq & \Delta + Nm E[|\epsilon_{1,t}^{1}|] \nonumber \\
\leq & \Delta + Nm \sqrt{\frac{2}{n\pi}} \nonumber
\end{align}

@@

Now we are ready to prove our first main result, Theorem~\ref{rst:budget}. \bccomment{Not sure if I used Lemma~\ref{lemma:payment} correctly.}

>>>>

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$. \bccomment{Our current analysis of the cumulative expected payment is wrong. See the comments of Lemma 6 for details}
\label{rst:budget}
\end{theorem}

@@

Denote $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$, then $X_{i}$ follows a ``geometric distribution'', which counts the total number of trials before the $i^{th}$ different arm were pulled at time $t=t^{0},t^{0}+1,\cdots$. At each time $t=t^{0}, t^{0}+1,\cdots$, there are two possibilities for a success trial:
\begin{itemize}
\item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $n^{-1}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled. In this case, the probability that the $i^{th}$ different arm will be pulled is 1.  
\item There exists at least $n^{-1}$ proportion of agents who will choose an un-pulled arm as his/her myopic action. In this case, the probability that the $i^{th}$ different arm will be pulled is at least $n^{-1}$.
\end{itemize}

@@

\begin{lemma}
For $t\in[t_n,t_{n+1}]$, the expected incentive payment $E[c(t)]$ is bounded above by $\Delta + 2WNm \sqrt{\frac{2}{n\pi}}$. 
\label{lemma:payment}
\end{lemma}

@@

\begin{align}
&E[c(t)] \nonumber \\
\leq & \Delta \times P(c(t)>0) + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\min_{j}\theta_t\cdot \epsilon_{j,t}1\{c(t)>0\}] \nonumber \\
\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\min_{j}\theta_t\cdot \epsilon_{j,t}] \nonumber \\
\leq & \Delta + \sum_{j=1}^{m}2WE[\max_{i}|\epsilon_{i,t}^{j}|] \nonumber \\
\leq & \Delta + 2W\sum_{j=1}^{m}E\left[\sum_{i=1}^{N}|\epsilon_{i,t}^{j}|\right] \nonumber \\
\leq & \Delta + 2WNm E[|\epsilon_{1,t}^{1}|] \nonumber \\
\leq & \Delta + 2WNm \sqrt{\frac{2}{n\pi}} \nonumber
\end{align}

@@

Now we are ready to prove our first main result, Theorem~\ref{rst:budget}. \bccomment{The current proof about the cumulative expected payment is wrong. We need to bound the $E[c(t)|\textit{our algorithm decides to incentivize}]$ instead of $E[c(t)]$. However, the analysis for the cumulative regret is correct}
